\documentclass{scrreprt}

%%% Sane encodings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%%% Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Support PDF properly
\usepackage{hyperref}

% Reducing easily detectable mistakes
\usepackage[l2tabu, orthodox, experimental]{nag}

% Better typography
\usepackage{microtype}

% We are writing in english
\usepackage[english]{babel}

% Mathy stuff
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{dsfont}

% Support for listy environments
\usepackage{enumitem}

% Newer and better clone of the Computer Modern font
\usepackage{lmodern}

%%% Configuration %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Create an index
\usepackage{makeidx}
\makeindex

\hypersetup{
	% Encode PDF strings in Unicode, not ASCII
	unicode,
}

%%% Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{commands}

%%% Looks %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\KOMAoption{fontsize}{10pt}
\KOMAoption{paper}{A4}
\KOMAoption{parskip}{half}

\hypersetup{
	% Do not draw boxes around links, colour them
	colorlinks,
}

%%% Metadata %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Stochastic Processes}
\author{Jonas Lenz}
\makeatletter
\hypersetup{
	pdfauthor=\@author,
	pdftitle=\@title,
}
\makeatother

\begin{document}
\maketitle
\chapter*{Motivation and Planned Topics}
Laws of nature are encoded by differential equations: ODEs, e.g. classical mechanics 
\begin{align*}
\partial_t^2 x(t)=-a(x(t))\partial_t x(t)+F(t,x(t))
\end{align*}
where $a$ is a friction coefficients and $F$ describes the force,
or PDEs e.g. electrodynamics or quantum mechanics.
The aim of this course is to describe ODEs with noise, for example with random force.
The simplest form of an ODE is
\begin{align}\label{eq:simpleform}
\partial_t X_t=b(t,X_t)+\sigma(t,X_t)\xi_t
\end{align}
where $b$ is a deterministic force (drift), $\sigma$ denotes the diffusion coefficient (tells how important the noise is) and as the most important part
$\xi_t$ is the white noise.
First question: what noise?
The \glqq natural\grqq\, approach is a random Fourier series:
\begin{align}
\xi_t^{(N)}\coloneqq \sum_{k=0}^N Y_k \cos(kt)+ \sum_{k=1}^N Z_k \sin(kt)~~~t\in [0,2\pi)
\end{align}
with $Y_k,Z_k \sim \mathcal{N}(0,1)$.
The limit $\lim\limits_{N\to \infty} \xi_t^{(N)}$ does \emph{not} exist and is called \glqq white noise\grqq.
Nevertheless, it exists as a tempered distributions.
A possible solution might be to integrate in time to improve convergence. For this we define
\begin{align}
B_t^{(N)}\coloneqq \int_0^t\xi_s^{(N)}~\mathrm{d}s=tY_0+\sum_{k=1}^N \frac{1}{k}(Y_k\sin(kt)-Z_k(\cos(kt)-1)).
\end{align}
Soon, we will see that this limit exists. It is called \glqq Brownian motion\grqq.
Assume in \eqref{eq:simpleform} that $\sigma(t,y)\equiv \sigma_0$ is constant. Then we can compute
\begin{align*}
X_t-X_0=\int_0^t \partial_s X_s~\mathrm{d}s\overset{\eqref{eq:simpleform}}{=}\int_0^t b(s,X_s)~\mathrm{d}s+\sigma_0 B_t.
\end{align*}
This equation at least makes sense but we don't know whether we can solve it.
If $\sigma$ is not constant, a term $\int_0^t\sigma(s,X_s)\xi_s~\mathrm{d}s$ appears.
In order to give sense to this integral we will introduce Ito-integrals or rough integrals.

\section*{Literature}
Schilling/Partsch: \glqq Brownian Motion\grqq

\chapter{Brownian Motion}
\begin{defi}
Let $(E,\Sigma)$ be a measurable space and $T$ a set.
A collection of $(E,\Sigma)$-valued random variables (RVs) $(X_t)_{t\in T}$ is called \emph{$E$-valued stochastic process (SP) with index set $T$}
\end{defi}
%TODO Kasten

\begin{exmpl}
\begin{enumerate}[label=(\alph*)]
\item $(E,\Sigma)=(\Rd,\mathcal{B}(\Rd))$ and $T=\R_{\geq 0}$ then a SP is called \emph{$\Rd$-valued, continuous-time SP},
\item $(E,\Sigma)=(\{-1,1\},\mathcal{P}(\{-1,1\}))$ and $T=\Z^d$, \glqq spin system\grqq\, ,
\item If $E$ is countable and $T=\N_0$ we speak of an \emph{time discrete SP}.
\end{enumerate}
\end{exmpl}

\begin{rem}
From a dynamical point of view, $(X_t)$ is a $t$-dependent quantity that changes with time, this is suitable for the first and third example.
From a global point of view, a SP is one RV with values in the space $\Omega=E^T=\{f\colon T\to E\}$.
In the first example this means to consider the whole \emph{path} $(X_t)_{t\geq 0}$ as one object.
In the second example, one \glqq spin configuration\grqq $\in \{-1,1\}^{\Z^d}$ is an element of $\Omega$.
Questions: $\sigma$-algebra? Existence?
\end{rem}

\begin{defi}
Let $\textbf{X}=(X_t)_{t\in T}$ be a SP where the state space $E$ is a group (e.g $E=\Rd$) and $T\subseteq \R$.
The set $(X_{s,t})_{s,t\in T}$ with $X_{s,t}\coloneqq X_t-X_s$ is called the \emph{increment process of $\textbf{X}$} or \emph{set of increments}.
A SP has \emph{independent increments} if for all $n\in \N$ and all $s_1<t_1\leq s_2 <t_2\leq \dots \leq s_n<t_n$ with $s_i,t_i \in T$, the RVs $(X_{s_i,t_i})_{1\leq i \leq n}$ are independent.
A SP has \emph{stationary increments} if for all $n\in \N$ and all $s_1<t_1\leq s_2 <t_2\leq \dots \leq s_n<t_n, r$ with $s_i,t_i,r \in T$, we have
\begin{align*}
(X_{s_i,t_i})_{i=1,\dots,n}\sim  (X_{s_i+r,t_i+r})_{i=1,\dots,n},
\end{align*}
i.e. equal in distribution. 
\end{defi}
%TODO Kasten

\begin{defi}
A $\Rd$-valued SP $\textbf{B}=(B_t)_{t \in \R_{\geq 0}}$ is called \emph{Brownian Motion} (BM) if 
\begin{enumerate}
\item[(B0)] $B_0(\omega)=0$ for almost all $w\in \Omega$,
\item[(B1)] $\textbf{B}$ has independent increments,
\item[(B2)] $\textbf{B}$ has stationary increments,
\item[(B3)] $B_t-B_s\eqqcolon B_{s,t}\sim B_{t-s}\sim \mathcal{N}(0,(t-s)I_d)$
\item[(B4)] The map $t\mapsto B_t(\omega)$ is continuous for all $\omega \in \Omega$.
\end{enumerate}
\end{defi}
%TODO Kasten

\begin{rem}
Interpretation of (B0)-(B4) in view of $B_t=\int_0^t \xi_s~\mathrm{d}s$.
\begin{enumerate}
\item[(B0)] $\int_0^0\xi_s~\mathrm{d}s=0$,
\item[(B1)] $B_t-B_s=\int_s^t \xi_r~\mathrm{d}r$ and $\xi_r \amalg (\xi_s)_{s\not =r}~~\forall r$
\item[(B2)] distribution of $\xi_r$ does not depend on $r$,
\item[(B3)] Central limit theorem and Riemann approximation,
\item[(B4)] $t\to \int_0^t f_s~\mathrm{d}s$ is continuous for all \glqq sensible\grqq\, functions $f$, in particular for $f=\xi$.
\end{enumerate}
\end{rem}

\begin{defi}
The \emph{Gaussian measure} $\mathcal{N}(m,\sigma^2)$ with \emph{mean} $m$ and \emph{variance} $\sigma^2$ is the probability measure on
$(\R,\mathcal{B}(\R))$ with Lebesgue density
\begin{align*}
g_{m\sigma^2}(x)=\frac{1}{\sqrt{2\pi \sigma^2}} \exp\left(-\frac{1}{2\sigma^2}(x-m)^2\right).
\end{align*}
\end{defi}

\begin{prop}
Let $X\sim \mathcal{N}(m,\sigma^2)$. Then
\begin{enumerate}[label=(\alph*)]
\item $\mathds{E}(X)=m, \mathds{V}(X)=\sigma^2$.
\item We have the \glqq Gaussian tail estimate\grqq
\begin{align*}
\frac{1}{\sqrt{2\pi}} \frac{C}{C^2+1}\mathrm{e}^{-\frac{C^2}{2}}\leq \mathds{P}(X-m\geq C \sigma)\leq \frac{1}{\sqrt{2\pi}} \frac{1}{C}\mathrm{e}^{-\frac{C^2}{2}},
\end{align*}
for all $C>0,\sigma>0$.
\item For $(m_k)_{k\in \N}\subseteq \R$, $m\in \R$, $(\sigma_k)_{k\in \N}\subseteq \R_{\geq 0}$, $\sigma\in \R_{\geq 0}$ we have:
$m_k\to m$ and $\sigma_k\to \sigma$ if and only if $\mathcal{N}(m_k,\sigma_k^2)\overset{\text{d}}{\to} \mathcal{N}(m,\sigma^2)$.
\end{enumerate}
\end{prop}

\begin{defi}
A $\Rd$-valued RV $X$ is called \emph{$d$-dimensional Gaussian} if for all linear $L\colon \Rd\to \R$ there exist $m,\sigma^2$ with $LX\sim \mathcal{N}(m,\sigma^2)$.
Explicitly: if $X=(X^1,\dots,X^d)$ this means that for all $a_1,\dots,a_d \in \R$ there exist $m,\sigma^2$ such that $\sum_{i=1}^d a_i X^i \sim \mathcal{N}(m,\sigma^2)$.
\end{defi}
\end{document}
